Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-16 patient-clinician-workshop/pccworkshop.tex

>>>>

\section{Using activity diaries}

We imagine integrated activity diaries to be used by both clinicans
and patients in several ways.  First, for nearly all types of
conditions, monitoring a person's overall daily activity and sleep
duration can easily indicate how much rest, exercise, exposure to
others, and the outside world he or she might be getting.  Daily
records of the time(s) that a person gets up, eats, works, exercises
and relaxes can be analysed by clincians for irregular behaviours or
habits that might be affecting a person's well-being. For more
specific conditions, daily measurements of a person's blood pressure,
blood oxidation, heart rate, breathing, weight, and galvanic skin
response could be useful for tracking progress along an clinician
prescribed intervention, recovery from illness, or onset of new
conditions, be used to pinpoint sources of prolonged stress.

Merely providing access to such activity records back to individuals
could have direct effects on people's behavior, motivation and
perceived well-being.  For example, just as asking individuals to
introspect and justify their opinions and feelings has been found to
be both disruptive and reinforcing of their opinions
\cite{wilson1989introspection}, allowing people to reflect upon their
historical records of their activities might help people realize or
change their minds about how or why they feel particular ways. We feel
that there is significant room for investigation here, and potential
for research pertaining to self motivation and improvement.
